The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-01 paper/ms.tex
paper: add description of name conventions

The TESS mission \citep{ricker_transiting_2015}, though designed for
other purposes, holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  More
quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
database indicates that $\approx 2\times10^5$ open cluster members
brighter than $T=16$ will be observed in the full-frame images over
the first two years of TESS observations.  The actual number may be
larger, as cluster membership catalogs are not yet complete, even at
these relatively bright magnitudes \citep[{\it
e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
% Our target list currently sits at $\approx 1.0\times10^6$ candidate
% young stars, perhaps one-third of which are bonafide cluster members
% (see \S~\ref{sec:starselection}).

@@

107{,}647 of these stars, or about
10\% of the collection, have cluster memberships reported by
multiple authors.  The largest number of stars come from
\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
(11.1\%).
Stars reported in multiple catalogs have all available reference information
concatenated.  
The resulting CDIPS target star list is given in Table~N.
The distribution of target star brightnesses is shown in
Figure~\ref{fig:cdips_targets}.

@@

The classifications we used assessed:
\begin{enumerate}
    \item {\it Photometric variability classification}. Designations include 
    tags for planet candidates, eclipsing binaries, instrumental variations, 
    stellar variations, and ``weirdos''.
    %
    \item {\it Cluster membership status}. By default, all light curves were 
    made for stars with at least one literature claim of cluster membership.  
    However, some of these claims pre-dated the availability of Gaia-DR2
    parallaxes or proper motions.
    We therefore re-assess the membership status on a case-by-case basis 
    through inspection of the available astrometry and photometry.
    Known asterisms are also omitted at this point
    \citep[{\it e.g.},][]{sulentic_revised_1973,kos_galah_2018}.
    %
    \item {\it Photometric blends}. Tags are created to highlight whether the 
    depth of the photometric signal shows a strong dependence on aperture 
    size, and also whether the in-transit minus the out-of-transit images 
    reveal that the source of variability is in fact far from the target star.
\end{enumerate}
The actual classifications were performed by LGB, JH, and JNW.
The \texttt{TagSpaces} software was used~--~an extremely helpful tool
for the purposes of easily assigning labels to documents.
An example vetting report for a planet candidate is described in
Appendix~\ref{appendix:vetreport}.

@@

>>>>

The TESS mission \citep{ricker_transiting_2015}, though designed for
other purposes, holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  More
quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
database indicates that $\approx 2\times10^5$ open cluster members
brighter than $T=16$ will be observed in the full-frame images over
the first two years of TESS observations.  The actual number may be
larger, as cluster membership catalogs are not yet complete, even at
these relatively bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
% Our target list currently sits at $\approx 1.0\times10^6$ candidate
% young stars, perhaps one-third of which are bonafide cluster members
% (see \S~\ref{sec:starselection}).

@@

107{,}647 of these stars, or about
10\% of the collection, have cluster memberships reported by
multiple authors.  The largest number of stars come from
\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
(11.1\%). %FIXME how many in PMS vs UMS?
Stars reported in multiple catalogs have all available reference information
concatenated.

To assign unique cluster names, we adopted the name matched against
\citet{Kharchenko_et_al_2013} whenever possible, following the
procedure described in Appendix~\ref{appendix:uniquenames}.  For
moving groups not identified in \citet{Kharchenko_et_al_2013}, we
adopted the constellation-based naming convention from
\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
the original catalog.  This process reduced 16,425 name permutations
down to 3,216 unique cluster names.  Though we have made every effort
to avoid duplicates, a small number may remain in this column, so we
advise inspection of the \texttt{cluster} and \texttt{reference}
columns rather than the \texttt{unique_cluster_name} column when
analyzing individual objects of interest.  Nonetheless, 87.7\% of the
$\sim$million unique target stars are matched to clusters within
\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
The remainder are mostly the young stars from \citet{zari_3d_2018}.

The resulting CDIPS target star list is given in Table~N.
The distribution of target star brightnesses is shown in
Figure~\ref{fig:cdips_targets}.

@@

The classifications we used assessed:
\begin{enumerate}
    \item {\it Photometric variability classification}. Designations include 
    tags for planet candidates, eclipsing binaries, instrumental variations, 
    stellar variations, and ``weirdos''.
    %
    \item {\it Cluster membership status}. By default, all light curves were 
    made for stars with at least one literature claim of cluster membership.  
    However, some of these claims pre-dated the availability of Gaia-DR2
    parallaxes or proper motions.
    We therefore re-assess the membership status on a case-by-case basis 
    through inspection of the available astrometry and photometry.
    Known asterisms are also omitted at this point
    \citep[{\it e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
    %
    \item {\it Photometric blends}. Tags are created to highlight whether the 
    depth of the photometric signal shows a strong dependence on aperture 
    size, and also whether the in-transit minus the out-of-transit images 
    reveal that the source of variability is in fact far from the target star.
\end{enumerate}
The actual classifications were performed by LGB, JH, and JNW.
The \texttt{TagSpaces} software was used~--~an extremely helpful tool
for the purposes of easily assigning labels to documents.
An example vetting report for a planet candidate is described in
Appendix~\ref{appendix:vetreport}.

@@

\section{Assigning unique names to each cluster}
\label{appendix:uniquenames}

In assigning a single unique cluster name to each star, we matched
against the \citet{Kharchenko_et_al_2013} name whenever possible,
since this was the largest available catalog, and it also included
homogeneous age determinations for many of the clusters.
To find the matching name, in order of precedence we
\begin{enumerate}[(i)]
  \item checked for direct string matches from
    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
  \item checked whether the SIMBAD online name resolving service had
    any direct string matches against \citet{Kharchenko_et_al_2013}
    clusters with determined parameters;
  \item checked for string matches in the full
    \citet{Kharchenko_et_al_2013} index (including clusters without
    determined parameters);
  \item searched for spatial matches between each star and cluster
    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
    In cases with multiple cluster matches, we ignored candidate
    matches to avoid assigning incorrect names;
  \item checked the WEBDA double name
    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
    and repeated (i)-(iv).
\end{enumerate}

A few edge-cases, including for instance sub-clusters within larger
star-forming complexes like in Sco-Cen or Collinder~33, were 
manually resolved to the extent feasible \citep[][give
detailed pictures of the complex morphologies that frequently arise in
very young star-forming
regions]{rizzuto_multidimensional_2011,saurin_isolating_2015}.

The procedure described above failed to yield matches for a few of the
infrared clusters identified by \citet{majaess_discovering_2013} and
included in the \citet{dias_proper_2014} catalog.
For these cases, we used the name given by \citet{dias_proper_2014}.

The Hyades and a number of other nearby moving groups were also
missed, since they were not in the \citet{Kharchenko_et_al_2013}
catalog.  For moving groups not identified in
\citet{Kharchenko_et_al_2013}, we adopted the constellation-based
naming convention from \citet{gagne_banyan_XI_2018}.

Finally, the procedure enumerated above did not yield matches for
recently discovered clusters, such as the ``RSG'' clusters found by
\citet{roser_nine_RSG_2016} and the ``Gulliver'' clusters from
\citet{cantat-gaudin_gaia_2018}.  In these cases, we used the names
given by the original authors.
